Who will win the US 2024 election?!!

### 2024-03-14 paper/paper.qmd
addded abstract

---
title: "Who will win the US 2024 election?!!"
subtitle: "My subtitle if needed"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Who will win the US 2024 election?!!"
subtitle: "My subtitle if needed"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour during the US presidential election in 2022 using
 data from the American Community Survey(ACS) 2022 sample.

 We look at the correlation between voting preferences and demographic, socioeconomic, and geographic factors,
 such as age, income, education, state of residency, and gender.

 Our study reveals complex trends and determinants of voting behaviour, providing understanding into the complex
 relationships between personal traits and local factors that influence election results.

 This research contributes to a better understanding of the factors influencing political engagement in American
 democracy by offering insightful information that might guide future electoral strategies and policy discussion."
 format: pdf
number-sections: true
bibliography: references.bib
---
